\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-26 docs/proposal/doc.tex
time schedule toegevoegd, stukje aan strategy toegevoegd

@@

\subsection*{Causal discovery methods}
The causal discovery method which we will use is the BCCD-algorithm.
This algorithm finds both the structure of a network as well as the direction of the connections of this network. This algorithm has some useful properties; it is a Bayesian approach and as such, it is robust against noise.
%It also does not need any assumptions beforehand.
The authors have shown the method to perform as good as or better than other causal discovery algorithms such as FCI and PC on representative datasets.
As is inherent to Bayesian methods, or approximations of Bayesian methods, the resulting network graph is not a  single structure but rather a distribution over possible structures.
Concretely, this provides an uncertainty measure over edges in the network, giving additional information compared to PC and FCI \cite{claassen2012}.

@@

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity. For this, implementations of PC and BCCD can be used. PC is a widely used algorithm and as such, many implementations already exist. An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university. The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset. This will result in a connectivity matrix which represents the effective connectivity. These results will  be evaluated by cross-subject comparison, to see whether the gained data is consistent. If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity. As PC is a state-of-the-art algorighm \cite{spirtes2000}, and BCCD shows a good potential \cite{claassen2012}, this way of determining effective connectivity may very well be the case.

@@

\section{Time schedule}

>>>>

% for coloring individual cells in a table
\usepackage[table]{xcolor}
%\usepackage{pgfgantt}

@@

\subsection*{Causal discovery methods}
The first causal method that we will use to find effective connectivity will be the PC-algorithm.
This is a state of the art used for general causal discovery, which finds the structure and the direction of connections of this network.
If a graph skeleton of a network is already known beforehand, this can also be used as a basis such that the PC-algorithm can determine the directions.
Another causal discovery method is the BCCD-algorithm \cite{claassen2012}, which gives similar results as PC.
This algorithm has some useful properties; it is a Bayesian approach and as such, it is robust against noise.
The authors have shown the method to perform as good as or better than other causal discovery algorithms such as FCI and PC on representative datasets.
As is inherent to Bayesian methods, or approximations of Bayesian methods, the resulting network graph is not a  single structure but rather a distribution over possible structures.
Concretely, this provides an uncertainty measure over edges in the network, giving additional information compared to PC and FCI.

@@

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity.
For this, implementations of PC and BCCD can be used.
PC is a widely used algorithm and as such, many implementations already exist.
An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university.

The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset.
We will first try the PC-algorithm, for which a suitable implementation still needs to be found. This will be done by using only functional connectivity data and also by providing strucural connectivity data as a graph skeleton.
The BCCD-algorithm will be used afterwards, which will also be used with only functional data as well as with functional and structural connectivity data.
This will result in a connectivity matrix which represents the effective connectivity.
These results will then be evaluated by cross-subject comparison, to see whether the gained data is consistent.
If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity.
As PC is a state-of-the-art algorighm \cite{spirtes2000}, and BCCD shows a good potential \cite{claassen2012}, this way of determining effective connectivity may very well be the case.

Two algorithms are used, and both are applied on two different forms of data: using either functional connectivity data only, or functional and structural connectivity data. Therefore four results will be obtained. If problems arise getting one of these results, we can still obtain enough data to draw useful conclusions.

@@

% week 50 is deadline voor draft, 51 is presentaties, 2 inleveren van final
% gantt gaf wat problemen met packages die nodig zijn om te compileren
% \section{Time schedule}
% \begin{ganttchart}{1}{10}
% \gantttitle{2011}{10} \\
% \gantttitlelist{40,...,52,1,2}{1} \\
% \ganttgroup{Group 1}{1}{7} \\
% \ganttbar{Task 1}{1}{2} \\
% \ganttlinkedbar{Task 2}{3}{7} \ganttnewline
% \ganttmilestone{Milestone}{7} \ganttnewline
% \ganttbar{Final Task}{8}{12}
% \ganttlink{elem2}{elem3}
% \ganttlink{elem3}{elem4}
% \end{ganttchart}

\section{time schedule}
For the time schedule, this project has been divided in four main parts: applying the PC-algorithm, applying the BCCD-algorithm, analysing the data (including cross-subject comparison) and writing the article. The schedule for applying the algorithm has been subdivided into applying it with functional connectivity data only, and applying it to both functional and structural connectivity data.

\begin{tabular}[ht]{c || c | c | c | c | c | c | c | c | c | c |}
\setlength{\tabcolsep}{12pt}
\renewcommand{\arraystretch}{1.3}
week          & 41 & 42 &  43 &  44 &  45 &  46 &  47 &  48 &  49 &  50 \tabularnewline \hline
PC            & \multicolumn{2}{ |c| }{\cellcolor[gray]{0.9} find implementation} & \multicolumn{2}{ |c| }{\cellcolor[gray]{0.9} functional}  & \cellcolor[gray]{0.9} structural  & \multicolumn{4}{ |c| }{} & \tabularnewline \hline
BCCD          & \multicolumn{4}{ |c| }{} & \multicolumn{2}{ |c| }{\cellcolor[gray]{0.85} functional} & \cellcolor[gray]{0.85} structural & \multicolumn{3}{ |c| }{} \tabularnewline \hline
analysis      & \multicolumn{3}{ |c| }{} & \multicolumn{2}{ |c| }{\cellcolor[gray]{0.9} PC} & & \multicolumn{2}{ |c| }{\cellcolor[gray]{0.9} BCCD} & \multicolumn{2}{ |c| }{} \tabularnewline \hline
write article & \multicolumn{3}{ |c| }{} & \multicolumn{7}{ |c| }{\cellcolor[gray]{0.85}}  \tabularnewline \hline
\end{tabular}
